Algorithm explanation

### 2013-04-24 article/algo.tex
Small changes

The Horn clause solving algorithm receives an input problem in Horn
graph. A Horn graph is a labelled directed graph $G=(V,E,\varphi)$,
where V is a set of vertices and E is a set of labelled
edges. $\varphi: V \rightarrow L$ is a labelling function for
vertices, where L is a set of elements of a predicate variable $P(x_1,
..., x_n)$ or a linear inequality $a_1 x_1 + \cdots + a_n x_n \leq b$.
An edge from a vertex $u$ to $v$ is expressed as a 3-tuple
$(u,v,\theta)$ where $\theta$ is a finite map from variables to
variables.

@@

Any model $\sigma$ to the constraint $C_{v_\bot}$ gives a simple
solution for $G$ if $C_{v_\bot}$ is satisfiable, i.e., we should have:

>>>>

The Horn clause solving algorithm receives an input problem in Horn
graph. A Horn graph is a labelled directed graph $G=(V,E,\varphi)$,
where V is a set of vertices and E is a set of labelled
edges. $\varphi: V \rightarrow L$ is a labelling function for
vertices, where L is a set of elements of a predicate variable $P(x_1,
..., x_{n_P})$ or a linear inequality $a_1 x_1 + \cdots + a_n x_n \leq
b$.  An edge from a vertex $u$ to $v$ is expressed as a 3-tuple
$(u,v,\theta)$ where $\theta$ is a finite map from variables to
variables.

@@

Any model $\sigma$ of the constraint $C_{v_\bot}$ gives a simple
solution for $G$ if $C_{v_\bot}$ is satisfiable, i.e., we should have:
